### 2013-09-28 manuscripts/dpp-msbayes/dpp-msbayes.tex
Working on results of dpp ms.

>>>>

The original \msb model \modelOld performs reasonably well when applied
to its own datasets (Figure \ref{figValidationModelChoiceOldOld}), but
it performs poorly when applied to data generated under any of the other
models (Figs.\
\labelcref{figValidationModelChoiceDPPOld,figValidationModelChoiceUniformOld,figValidationModelChoiceUshapedOld}).
In these cases the \modelOld model is strongly biased towards over-estimating
the posterior probability of the one-divergence model, especially when the
divergence models are not distributed under its U-shaped prior (Figs.\
\labelcref{figValidationModelChoiceDPPOld,figValidationModelChoiceUniformOld}).
The other model with the U-shaped prior on divergence models, but exponential
priors on nuisance parameters (\modelUshaped), performs similarly to \modelOld
in that it performs well when applied to its own data, but overestimates
the probability of the one-divergence model when applied to data generated
by the other models (Figs.\
\labelcref{figValidationModelChoiceDPPUshaped,figValidationModelChoiceUniformUshaped,figValidationModelChoiceUshapedUshaped,figValidationModelChoiceUshapedUshaped}).
However, the bias toward over-estimating the probability of the one-divergence
model is stronger in the \modelOld model than \modelUshaped.

Overall, the result suggest that the \modelDPP and \modelUniform models are
relatively robust in terms of model-choice accuracy, and when model violations
do cause them to be biased, they tend to under-estimate the probability of
the biogeographically interesting model of a single divergence event.
In contrast, the \modelOld model is very sensitive to model violations,
and strongly over-estimates the one-divergence model whenever the model
is misspecified.
Furthermore, the results suggest that using exponentially distributed priors on
nuisance parameters rather than uniform priors helps the \modelUshaped model
perform better than \modelOld, but it is still hindered by the Ushaped prior on
divergence models and tends to over-estimate the probability of the
one-divergence model whenever there are violations of the mode.

\subsection*{Validation analyses: Ordered divergence models}
Our results show that the model estimating ordered models of divergence
\modelDPPOrdered performs similarly to its counterpart sampling over
unordered models \modelDPP when the prior is correct (Figs.\
\labelcref{figValidationAccuracyDPPOrderedDPPOrdered,figValidationModelChoiceDPPOrderedDPPOrdered}).
